### 2013-09-30 chi2014/qualitative.tex
personas

Two time-saving strategies were also identified. The first, perhaps overly obvious strategy, is \emph{brevity}. This is simply the act of keeping responses as concise as possible, presumably in the interest of finishing quickly. The second time-saving strategy was \emph{cop-outs}. Cop-outs occur when participants choose to resort to vague and unsatisfying responses that do not actually provide any solution to the problem. For example, one participant's response to the MP3 player problem was to "Remove glass screen to make something". Cop-out responses may provide one or more steps towards a solution, but no solution.

>>>>

Two time-saving strategies were also identified. The first, perhaps overly obvious strategy, is \emph{brevity}. This is simply the act of keeping responses as concise as possible, presumably in the interest of finishing quickly. The second time-saving strategy was \emph{cop-outs}. Cop-outs occur when participants choose to resort to vague or iunrelated responses that do not actually provide any solution to the problem. For example, one participant's response to the MP3 player problem was to "Remove glass screen to make something". Cop-out responses may provide one or more steps towards a solution, but no solution.

\subsection{Personas}

We use personas to capture collections of strategy use we see repeated across participants. While some strategies proved discriminatory, others were used more or less equally by all personas. Drill-down riffing, pairing and language riffing, while interesting strategies, are either minimal in the makeup of a run or have no impact of the subjective quality of the resulting ideas.

Six personas were identified: quitters, lazy creatives, diligent struggles, lazy strugglers, hard workers, and over-deliverers.

\emph{Quitters} are the easiest to summarize. These participants do not provide all the requested responses, and often resort to cop-outs or exhaustive mutation in the ideas that they do provide.

\emph{Lazy creatives} provide primarily uncommon responses, but do not put any particular effort into the responses. They employ the brevity, reach back and exhaustive mutation strategies to a great extent. These participants seem like prime targets for future interventions, as their ideas are of interest but they focus their strategies towards rapid completion. Lazy creatives employ minimal feature utilization.

\emph{Diligent strugglers} are the opposite of lazy creatives. These participants do not employ the brevity or exhaustive mutation strategies, but nonetheless produce primarily common, unoriginal ideas. These participants also seem like potential targets for interventions, as they apply themselves to the task but may need external assistance to move beyond their comfort zone. Strategies employed include exploratory riffing and feature utilization.

\emph{Lazy strugglers} are simply those who produce no creative ideas and are predisposed towards unproductive strategies (primarily exhaustive mutation and brevity).

\emph{Hard workers} are notable for their minimal use of riffing strategies. The riffing strategies they do use tend to exclude exhaustive mutation. While brevity is occasionally employed for short periods, it is generally only where a short description is sufficient to communicate an idea.

\emph{Over-deliverers} are notable for their lack of strategy in general. Their ideas are verbose, distinct and feature extremely minimal riffing.
